---
title: Homework 2
author: Hunter Rose, hrose33
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r}
cel <- c((24-31*(5/9)), (15-32*(5/9)))
cel
```
```{r}
vec200 <- 0
for(i in 1:200){
  if((i%%2)==0)
    vec200[i] = 1
  else
    vec200[i] = 3
}
vec200
```
```{r}
numPerfect <- 0
for(i in 1:2001){
  x <- 1
  while((x*x)<=i){
    if((x*x)==i)
      numPerfect = numPerfect+1
    x <- x+1
  }
  i <- i+1
}
numPerfect
```
```{r}
mpg <- ggplot2::mpg
top3 <- mpg[order(-mpg[, "hwy"]),]
top3[1:3,]
```

```{r}
comp <- subset(mpg, class == "compact")
numCompact <- nrow(comp)
numCompact
```

```{r}
ggplot(mpg, aes(x = cty,y = hwy)) + geom_point()
```



The relationship between city and highway mileage is positively linear. This is because a car with a high city mileage will also have a high highway mileage.
The reason that there is so few points is because there are cars with the same mileage in both city and highway and they are being grouped together. 

```{r}
cars_08 <- subset(mpg, year == 2008)
cars_99 <- subset(mpg, year == 1999)
ggplot(cars_08, aes(x = cty, y = hwy)) + geom_point()
summary(cars_08)
ggplot(cars_99, aes(x = cty, y = hwy)) + geom_point()
summary(cars_99)
```
After looking over the data, cars manufactured in 1999 have a slightly better average city mileage(17.02) compared to cars manufactured in 2008(16.7). Although cars manufactured in 1999 are have the advantage in city, they have a smaller average highway mileage(23.43) compared to the 2008 cars(23.45). Since the difference between highway mileage is only .02 in 2008 cars favor, and the difference between city mileage is .32 in 1999 cars favor, I would say that cars manufactured in 1999 have better mileage.


```